---
title: "Problem Set 1"
author: "Sarah Tmimi, Lesley Thomas,  Andrew Walsh"
date: "2/2/2019"
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    toc_float: true
    toc_collapsed: true
    theme: journal
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loadpackages, warning=FALSE, messages=FALSE, error=FALSE} 
library(ggplot2)
library(dplyr)
```

## Part 1 
## Hello this is Andrew
###Question 1 
steps to changing R studio to Black:

  1. Tools 
  2. Global Options 
  3. Appearance 
  4. Editor Theme 
  5. Chaos (or any of the first 3 themes)
  
###Question 2
finding R packages: 
  
  1. downloading the text posts of twitter
  2. load an SPSS data file 
  3. Annotate street maps 
  4. download the text of *The adventures of Sherlock Holms*
  5. scrape the text off of webpages 
  6. create an animated movie to show how a scatter plot changes over time
  
###Question 3 
cleaning up a code chunk: 

```{r firstcode, fig.width=6, fig.height=4, fig.align="center"}
ggplot(mtcars, 
       aes(x=mpg, y=qsec,color=
             factor(am))) + geom_point() +
  geom_smooth(method="loess", se=FALSE) +
  xlab("Miles per gallon") + 
  ylab("1/4 mile time") +
  guides(color=guide_legend(title=
  "Transmission")) +
  scale_color_manual(labels =
  c("Automatic", "Manual"), values =
    c("blue", "red")) + 
  ggtitle("Speed vs. Mileage")
```
  
##Part 2 
###Question 1 

```{r objects}
uvawins <- 19 

#a 
sqrt(uvawins)

#b
uvawins^3 

#c
log(uvawins)

#d
exp(uvawins)

#e
log10((4*(uvawins-5))/9)
```
###Question 2 

```{r temps}
temps <- c(45, 51, 52, 39, 40, 45, 38)

#a
temps[4]

#b
((temps - 32)*5)/9
```

###Question 3 

```{r weekdays}
days <- c("sunday", "monday", "tuesday", "wednesday", "thursday", "friday", "saturday")

days_temps <- data.frame(days, temps)

days_temps

```

###Question 4 
```{r imdbdata}
setwd("~/Desktop/PLAD 4500")
imdb <- read.csv("imdb.csv")
```

###Question 5 
```{r imdbvars}
names(imdb)
```

###Question 6 
```{r imdbmean}
summary(imdb$imdb_score)

```
the mean imdb score is 6.442

###Question 7????


###Question 8 
```{r imdbclass}

str(imdb$movie_title)

```
`movie_titles` are a factor class. This is not a good choice for this variable because factors are for categories, but movie titles are words, so it should be a character class. 

###Question 9

```{r imdbcoerce}

 ### not sure how to reference a variable??
imdb <- as.character("movie_titles")
```

##Part 3: Getting Help 

###Question 1

to change the confidence interval displayed by the function `geom_smooth()` from it's default of a 95% confidence interval to an 80% confidence interval you would type `level=.80` in parentheses after the command. 

###Question 2 ??
why is <- better than = ???

###Question 3 ??

###Question 4 ??


<iframe width="560" height="315" src="https://www.youtube.com/watch?v=-aqsOl_3AMQ" allowfullscreen></iframe>

###Question 5 

  1. you're clearly asking a homework question and people don't like when you do that 
  2. you haven't included any information about what you've already tried to solve the problem yourself
  3. didn't include the version of R you're using/ what operating system you have

