---
title: "Problem Set 1"
author: "Sarah Tmimi, Lesley Thomas,  Andrew Walsh"
date: "2/2/2019"
output: 
  html_document:
    toc: TRUE
    toc_depth: 4
    toc_float: true
    toc_collapsed: true
    theme: journal
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loadpackages, warning=FALSE, messages=FALSE, error=FALSE} 
library(ggplot2)
library(dplyr)
```

## Part 1 
##How to use git
## to add your code to the 'cloud'
## git add .
## git commit -m"1"
## git push origin master

## to download the code from the cloud
## git stash
## git pull origin master
###Question 1 
steps to changing R studio to Black:

  1. Tools 
  2. Global Options 
  3. Appearance 
  4. Editor Theme 
  5. Chaos (or any of the first 3 themes)
  
###Question 2
finding R packages: 
  
  1. downloading the text posts of twitter
    Found the package 'twitteR' by googling for packages that can get text posts from twitter. It implements the entire Twitter API in R, and lets you do things like look at DM's, friends, posts, search, and more. https://cran.r-project.org/web/packages/twitteR/twitteR.pdf
    
  2. load an SPSS data file
I googled how to "load an SPSS data file" and found the website statmethods.net which recommended using the package 'Hmisc' to load an SPSS data file. The package can also provide functions for data analysis, advanced table making, conversion of R objects to LaTeX and html code and more. 
https://cran.r-project.org/web/packages/Hmisc/index.html

  3. Annotate street maps
   found the package `ggmaps` by googling "annotating street maps r package". The package is a collection of functions for vizualizing spatial data from online sources, and includes functions for geolocation and routing https://cran.r-project.org/web/packages/ggmap/ggmap.pdf
   
  4. download the text of *The adventures of Sherlock Holms*
  Found a package called 'gutenbergr' by googling for packages that can download sherlock holmes. It can download public domain works, information about the works and authors, and 'pairings' of work in the Library of Congress. https://cran.r-project.org/web/packages/gutenbergr/vignettes/intro.html
  
  5. scrape the text off of webpages 
  I found the package 'rvest' through google, which brought me to a beginner's guide for Web Scraping. The webpage suggested using rvest to easily download and then manipulate HTML and XML.
https://cran.r-project.org/web/packages/rvest/index.html

  6. create an animated movie to show how a scatter plot changes over time
   found the package `gganimate` by googling "r package for creating an animated movie to show how a scatter plot changes over time". This package wraps aroung ggplot to create animated ggplots. https://www.rdocumentation.org/packages/gganimate/versions/0.1.1
  
###Question 3 
cleaning up a code chunk: 

```{r firstcode, fig.width=6, fig.height=4, fig.align="center"}
ggplot(mtcars, aes(x=mpg, y=qsec,color=factor(am))) + 
  geom_point() +
  geom_smooth(method="loess", se=FALSE) +
  xlab("Miles per gallon") + 
  ylab("1/4 mile time") +
  guides(color=guide_legend(title="Transmission")) +
  scale_color_manual(labels = 
    c("Automatic", "Manual"), values = c("blue","red")) + 
  ggtitle("Speed vs. Mileage")
```

##Part 2 
###Question 1 

```{r objects}
uvawins <- 20

#a 
sqrt(uvawins)

#b
uvawins^3 

#c
log(uvawins)

#d
exp(uvawins)

#e
log10((4*(uvawins-5))/9)
```
###Question 2 

```{r temps}
temps <- c(45, 51, 52, 39, 40, 45, 38)

#a
temps[4]

#b
((temps - 32)*5)/9
```

###Question 3 

```{r weekdays}
days <- c("sunday", "monday", "tuesday", "wednesday", "thursday", "friday", "saturday")

days_temps <- data.frame(days, temps)

days_temps

```

###Question 4 
```{r imdbdata}
##setwd("~/Desktop/PLAD-4500-PS1")
imdb <- read.csv("imdb.csv")
```

###Question 5 
```{r imdbvars}
names(imdb)
```

###Question 6 
```{r imdbmean}
summary(imdb$imdb_score)

```
the mean imdb score is 6.442

###Question 7????


###Question 8 
```{r imdbclass}

str(imdb$movie_title)

```
`movie_titles` are a factor class. This is not a good choice for this variable because factors are for categories, but movie titles are words, so it should be a character class. 

###Question 9

```{r imdbcoerce}

 ### not sure how to reference a variable??
imdb <- as.character("movie_titles")
```

##Part 3: Getting Help 

###Question 1

to change the confidence interval displayed by the function `geom_smooth()` from it's default of a 95% confidence interval to an 80% confidence interval you would type `level=.80` in parentheses after the command. 

###Question 2 ??
why is <- better than = ???

###Question 3 ??

###Question 4 ??


<iframe width="560" height="315" src="https://www.youtube.com/watch?v=-aqsOl_3AMQ" allowfullscreen></iframe>

###Question 5 

  1. you're clearly asking a homework question and people don't like when you do that 
  2. you haven't included any information about what you've already tried to solve the problem yourself
  3. didn't include the version of R you're using/ what operating system you have

